### 2024-08-11 download-football-data.qmd
20240811 - fantasy football projections

# Downloaded Data - Raw
load(file = "./data/nfl_players_raw.RData")
load(file = "./data/nfl_teams_raw.RData")
load(file = "./data/nfl_rosters_raw.RData")
load(file = "./data/nfl_rosters_weekly_raw.RData")
load(file = "./data/nfl_schedules_raw.RData")
load(file = "./data/nfl_combine_raw.RData")
load(file = "./data/nfl_draftPicks_raw.RData")
load(file = "./data/nfl_depthCharts_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation_raw.RData", fsep = ""))
load(file = "./data/nfl_actualStats_weekly_raw.RData")
load(file = "./data/nfl_injuries_raw.RData")
load(file = "./data/nfl_snapCounts_raw.RData")
load(file = "./data/nfl_espnQBR_seasonal_raw.RData")
load(file = "./data/nfl_espnQBR_weekly_raw.RData")
load(file = "./data/nfl_nextGenStats_weekly_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly_raw.RData")
load(file = "./data/nfl_playerContracts_raw.RData")
load(file = "./data/nfl_ftnCharting_raw.RData")
load(file = "./data/nfl_playerIDs_raw.RData")
load(file = "./data/nfl_rankings_draft_raw.RData")
load(file = "./data/nfl_rankings_weekly_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp_raw.RData", fsep = ""))

@@

# Downloaded Data - Processed
load(file = "./data/nfl_players.RData")
load(file = "./data/nfl_teams.RData")
load(file = "./data/nfl_rosters.RData")
load(file = "./data/nfl_rosters_weekly.RData")
load(file = "./data/nfl_schedules.RData")
load(file = "./data/nfl_combine.RData")
load(file = "./data/nfl_draftPicks.RData")
load(file = "./data/nfl_depthCharts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation.RData", fsep = ""))
load(file = "./data/nfl_actualStats_weekly.RData")
load(file = "./data/nfl_injuries.RData")
load(file = "./data/nfl_snapCounts.RData")
load(file = "./data/nfl_espnQBR_seasonal.RData")
load(file = "./data/nfl_espnQBR_weekly.RData")
load(file = "./data/nfl_nextGenStats_weekly.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly.RData")
load(file = "./data/nfl_playerContracts.RData")
load(file = "./data/nfl_ftnCharting.RData")
load(file = "./data/nfl_playerIDs.RData")
load(file = "./data/nfl_rankings_draft.RData")
load(file = "./data/nfl_rankings_weekly.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp.RData", fsep = ""))

@@

@@

@@

@@

@@

@@

nfl_expectedFantasyPoints_pbp <- full_join(
  nfl_expectedFantasyPoints_pass_raw,
  nfl_expectedFantasyPoints_rush_raw,
  by = c("game_id","fixed_drive","play_id"),
  suffix = c(".pass", ".rush")
)

# Todo:
#-separate variables from each pass/rush object
```

@@

@@

>>>>

# Downloaded Data - Raw
load(file = "./data/nfl_players_raw.RData")
load(file = "./data/nfl_teams_raw.RData")
load(file = "./data/nfl_rosters_raw.RData")
load(file = "./data/nfl_rosters_weekly_raw.RData")
load(file = "./data/nfl_schedules_raw.RData")
load(file = "./data/nfl_combine_raw.RData")
load(file = "./data/nfl_draftPicks_raw.RData")
load(file = "./data/nfl_depthCharts_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation_raw.RData", fsep = ""))
load(file = "./data/nfl_actualStats_weekly_raw.RData")
load(file = "./data/nfl_injuries_raw.RData")
load(file = "./data/nfl_snapCounts_raw.RData")
load(file = "./data/nfl_espnQBR_seasonal_raw.RData")
load(file = "./data/nfl_espnQBR_weekly_raw.RData")
load(file = "./data/nfl_nextGenStats_weekly_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly_raw.RData")
load(file = "./data/nfl_playerContracts_raw.RData")
load(file = "./data/nfl_ftnCharting_raw.RData")
load(file = "./data/nfl_playerIDs_raw.RData")
load(file = "./data/nfl_rankings_draft_raw.RData")
load(file = "./data/nfl_rankings_weekly_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp_raw.RData", fsep = ""))
load(file = "./data/players_projections_seasonal_raw.RData")

@@

# Downloaded Data - Processed
load(file = "./data/nfl_players.RData")
load(file = "./data/nfl_teams.RData")
load(file = "./data/nfl_rosters.RData")
load(file = "./data/nfl_rosters_weekly.RData")
load(file = "./data/nfl_schedules.RData")
load(file = "./data/nfl_combine.RData")
load(file = "./data/nfl_draftPicks.RData")
load(file = "./data/nfl_depthCharts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation.RData", fsep = ""))
load(file = "./data/nfl_actualStats_weekly.RData")
load(file = "./data/nfl_injuries.RData")
load(file = "./data/nfl_snapCounts.RData")
load(file = "./data/nfl_espnQBR_seasonal.RData")
load(file = "./data/nfl_espnQBR_weekly.RData")
load(file = "./data/nfl_nextGenStats_weekly.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly.RData")
load(file = "./data/nfl_playerContracts.RData")
load(file = "./data/nfl_ftnCharting.RData")
load(file = "./data/nfl_playerIDs.RData")
load(file = "./data/nfl_rankings_draft.RData")
load(file = "./data/nfl_rankings_weekly.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp.RData", fsep = ""))
load(file = "./data/players_projections_seasonal_average.RData")

@@

#### Processing {#sec-processingPlayers}

@@

#### Processing {#sec-processingRosters}

@@

#### Processing {#sec-processingDraftPicks}

@@

#### Processing {#sec-processingDepthCharts}

@@

#### Processing {#sec-processingAdvancedStatsPFR}

@@

nfl_expectedFantasyPoints_pbp <- full_join(
  nfl_expectedFantasyPoints_pass_raw,
  nfl_expectedFantasyPoints_rush_raw,
  by = c("game_id","fixed_drive","play_id"),
  suffix = c(".pass", ".rush")
)
```

@@

#### Processing {#sec-processingExpectedFantasyPoints}

@@

### Fantasy Football Projections {#sec-fantasyFootballProjections}

#### Download Players' Projections {#sec-scrapeProjections}

::: {#nte-downloadProjections .callout-note title="Downloading players' seasonal projections"}
Note: the following code takes a while to run.
:::

players_projections_seasonal_raw <- ffanalytics::scrape_data(
  season = NULL, # NULL grabs the current season
  week = 0) # NULL grabs seasonal projections; NULL grabs the current week
```

save(
  players_projections_seasonal_raw,
  file = "./data/players_projections_seasonal_raw.RData"
)
```

The data file is saved in the project repository and can be loaded using the following command:

load(file = "./data/players_projections_seasonal_raw.RData")
```

The `players_projections_seasonal_raw` object is in `player`-`position`-`projection source` form.
That is, each row should be uniquely identified by the combination of `id`, `pos`  and `data_src`.
Each row should also be uniquely identified by the combination of `player`, `pos`, and `data_src`.

Let's check for duplicate `player`-`position`-`projection source` instances:

```{r}
players_projections_seasonal_raw %>% 
  bind_rows() %>% 
  select(id, pos, data_src, everything()) %>%
  arrange(player, id, pos, data_src) %>% 
  group_by(id, pos, data_src) %>% 
  filter(n() > 1, !is.na(id)) %>% 
  head()

players_projections_seasonal_raw %>% 
  bind_rows() %>% 
  select(player, pos, data_src, everything()) %>%
  arrange(player, id, pos, data_src) %>% 
  group_by(id, pos, data_src) %>% 
  filter(n() > 1, !is.na(id)) %>% 
  head()
```

#### Specify League Scoring Settings {#sec-leagueScoringSettings}

First, create a scoring object using the default scoring object:

```{r}
scoring_obj_default <- ffanalytics::scoring
```

View the default scoring settings:

```{r}
scoring_obj_default
```

Now, modify the scoring settings to match our league settings:

```{r}
scoring_obj <- scoring_obj_default

scoring_obj$pass$pass_int <- -2
scoring_obj$misc$fumbles_lost <- -2
scoring_obj$idp$idp_fum_force <- -2
```

View our scoring settings:

```{r}
scoring_obj
```

#### Calculate Projected Points {#sec-calculateProjectedPoints}

```{r}
players_projectedStats_seasonal <- ffanalytics::projections_table(
  players_projections_seasonal_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = TRUE)

players_projectedPoints_seasonal <- ffanalytics::projections_table(
  players_projections_seasonal_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = FALSE)
```

The `players_projectedStats_seasonal` and `players_projectedPoints_seasonal` objects are in `player`-`average type`-`position` form.
That is, each row should be uniquely identified by the combination of `id`, `avg_type`  and `pos` (or `position`).

Let's check for duplicate `player`-`position`-`projection source` instances:

```{r}
players_projectedPoints_seasonal %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()

players_projectedStats_seasonal %>% 
  group_by(id, avg_type, position) %>% 
  filter(n() > 1) %>% 
  head()
```

Let's merge the two objects.

```{r}
players_projections_seasonal_average <- full_join(
  players_projectedPoints_seasonal,
  players_projectedStats_seasonal,
  by = c("id","avg_type","pos" = "position")
)
```

Let's again check for duplicate `player`-`position`-`projection source` instances:

```{r}
players_projections_seasonal_average %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()
```

#### Add Additional Player Information {#sec-addAdditionalInfo}

players_projections_seasonal_average <- players_projections_seasonal_average %>% 
  add_ecr() %>% 
  add_adp() %>% 
  add_aav() %>%
  add_uncertainty() %>% 
  add_player_info()
```

save(
  players_projections_seasonal_average,
  file = "./data/players_projections_seasonal_average.RData"
)
```

The data file is saved in the project repository and can be loaded using the following command:

```{r}
load(file = "./data/players_projections_seasonal_average.RData")
```

### 2024-08-11 fantasy-football.qmd
20240811 - fantasy football projections

| Statistical category          | Points |
|-------------------------------|--------|
| Defensive or special teams TD | 3      |
| Interception                  | 2      |
| Fumble recovery               | 2      |
| Blocked punt, PAT, or FG      | 2      |
| Safety                        | 2      |
| Sack                          | 1      |

>>>>

| Statistical category          | Points |
|-------------------------------|--------|
| Defensive or special teams TD | 6      |
| Interception                  | 2      |
| Fumble recovery               | 2      |
| Blocked punt, PAT, or FG      | 2      |
| Safety                        | 2      |
| Sack                          | 1      |
